### 2015-07-09 text/ms.Rmd
Edits to paper
- includes Kristin's edits

\noindent
^5^NOAA/NMFS/NEFSC, Ecosystem Assessment Program, 
Woods Hole, MA, 02543, USA

@@

Ecological resource managers are often faced with reconciling multiple potentially
conflicting estimates of population status and trajectory.  One solution is to
average these predictions in an ensemble, but this approach ignores covariance
between models and may not optimally reduce bias and improve accuracy.
Superensemble models, commonly used in the fields of climate and weather
science, may provide a superior solution. Superensembles use the predictions
from multiple models as covariates in a new statistical model. Here we evaluate
the potential for ensemble and superensemble models ('ensemble methods') to improve estimates of fish population
status and trajectory. We fit four models of population and exploitation
dynamics to data-limited populations and combine their estimates of the mean and
slope of biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with an
ensemble average and three superensembles: a linear model, a random forest, and
a boosted regression tree. We build our models on a simulated dataset of 5760
fish stocks and test them with cross-validation and a global database of 
`r ram_stocks_n` stock assessments. 
We find that ensemble methods
substantially improve estimates of population status and trajectory.
Machine-learning superensembles performed the best for population status: accuracy improved
`r mean_sim$mach_vs_ind_mare_fold`%, correlation between predicted and true
status improved from 
`r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median
proportional error) declined from 
`r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. 
We found similar improvements when predicting the trajectory of status. When the
simulation-trained superensembles were applied to global fish stocks, the best
models still improved all dimensions of performance over the next-best
individual model. Ensemble methods have the potential to
improve estimates of population status and trajectory across many taxa beyond
fish. However, they must be carefully tested, formed from a diverse set of
accurate models, and built on a dataset sufficiently representative of the
populations they are applied to.

@@

**Note if you're editing this: I recently started reworking the paper to
incorporate 'superensembles' as a term and focus on management/conservation need
up front instead of methods. As a result, some parts (mostly the introduction)
are still in rough draft form.**

\noindent Ecological population status and trajectory are two of the most
fundamental values to quantify in ecological resource management [e.g.
@mace2008]. Population status and trajectory are key to everything from global
assessments of extinction risk [e.g. @stuart2004; @schipper2008;
@juan-jorda2011] to local management of hunting (REF) and fishing (REF). But
ecological resource managers are often faced with reconciling multiple
uncertain and potentially conflicting estimates of these quantities. For
example, some models may suggest a population is at risk and declining in
abundance while others may suggest it is not at risk and stable (e.g. REF).

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased than
individual model estimates and can integrate uncertainty in model structure,
initial conditions, and parameter estimation [@araujo2007]. For instance,
REF-IUCN did this and REF-COSEWIC did this...

Whereas averages or weighted averages can improve predictions, they may not
optimally leverage available data. The truth does not necessarily lie in the
middle of multiple model predictions, some models perform better than others in
certain conditions, and the covariance between model predictions may contain
information that can improve predictions. We can exploit these characteristics
by using the predictions from a group of models as inputs into a separate
statistical model. This technique, sometimes called 'superensemble' modelling,
is common in climate and weather forecasting [@krishnamurti1999]. The
superensemble is fit to some training dataset where outcomes are well known and
used to predict on a dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

@@

In fisheries science, a number of models have been proposed to assess
population status (biomass compared to biomass at maximum sustainable yield,
$B/B_\mathrm{MSY}$) and trajectory based on the limited data available for the
majority of stocks: catches and a basic understanding of population
productivity [e.g. @vasconcellos2005; @martell2013]. Recently, @rosenberg2014
investigated the performance of four such models through a large-scale
simulation experiment. The four models frequently disagreed about population
status and any one model had relatively poor predictive ability on average
(e.g. Fig. \ref{motivate}).

Here, we estimate population status and trajectory of exploited fish
populations using ensembles and superensembles (collectively 'ensemble
methods') of these four data-limited models. We explore a variety of approaches
applied to both simulated and real-world fish stocks and compare predictive
performance. We find that ensembles, and in particular superensembles,
generally improved predictive performance of status and trajectory of fish
populations over any single model---especially when considered across multiple
dimensions of predictive ability and across multiple datasets. Furthermore, the
output from superensembles can aid mechanistic understanding of how individual
models of status and trajectory perform.

@@

We first developed and tested ensemble methods with a fully factorial simulated
dataset [@rosenberg2014]. These previously published simulation models included
three life histories: small pelagic, demersal, large pelagic; three levels of
how depleted biomass was at the start of the dataset compared to carrying
capacity: 100%, 70%, and 40% of carrying capacity; and four exploitation
dynamics: a constant exploitation rate, a exploitation rate that is coupled
with biomass to mimic an open-access single-species fishery, a scenario where
exploitation rate increases to a fixed level, and a 'roller-coaster' scenario
where the exploitation rate increases and then decreases. Process noise was
introduced to the models through two levels of multiplicative recruitment
variability: $N(0, 0.2)$ and $N(0, 0.6)$, and that process noise was either
uncorrelated or had a first-order autoregressive correlation of 0.6. The
simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year,
$B_t$ represents biomass at time $t$, $r$ represents the intrinsic population
growth rate, $B_0$ represents unfished biomass or carrying capacity, and $C$
represents catch. @rosenberg2014 provide a full summary of
these four methods and code to fit all the models is available in an
accompanying package `datalimited` for the statistical software \textsf{R}. In
summary:

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer
  biomass dynamics [@martell2013]. It requires a prior distribution for $r$ and
  assigns a prior to the relative proportion of biomass at the end compared to
  unfished biomass (depletion) based on the percentage of maximum catch at the
  end of the time series.

@@

$$
\hat{\theta} = 
\argmin_\theta \left( L(b \, | \, \hat{b}_{\mathrm{ensemble}}) \right)
$$
$$
\hat{b}_\mathrm{ensemble} = 
f \left( \hat{b}_\mathrm{CMSY}, \, \hat{b}_\mathrm{COM-SIR}, \,
\hat{b}_\mathrm{SSCOM}, \, \hat{b}_\mathrm{mPRM}, \,
S(0.2), \, S(0.5), \, | \, \theta \right)
$$

@@

We fit the linear model ensemble with second-order interactions. We fit two
machine learning ensemble models based on regression trees. Regression trees
sequentially determine what value of a predictor best splits the response data
into two 'branches' based on a specified loss function [@breiman1984]. In random
forests, a series of regression trees are built on a random subset of the data
and random subset of the covariates of the model [@breiman2001]. In generalized
boosted models (GBMs), each subsequent model is fit to the residuals from the
previous model; data points that are fit poorly in a given model are given more
weight in the next model [@elith2008]. Random forests and GBMs can provide
strong predictive performance and fit highly non-linear relationships
[@elith2008; @hastie2009]. We fit random forest models with the `randomForest`
package [@liaw2002] for \textsf{R} with the default argument values. We fit
boosted regression tree models with the `gbm` package [@ridgeway2015] for
\textsf{R}. Based on cross-validation with the **caret** \textsf{R} package, we
fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate
(shrinkage parameter) of $0.01$, and all other arguments at their default
values.

@@

A critical component to any predictive modelling exercise is to evaluate the
performance of a model on new data [@hastie2009]. We used repeated three-fold
cross validation to test predictive performance: we randomly divided the
dataset into three sets, built ensemble models on two-thirds of the data, and
evaluated predictive performance on the remaining third. We repeated this
across each of the three splits and then repeated the whole procedure 50 times
to account for bias that may result from any one set of validation splits.
Since the dynamics of simulated populations differing only in the stochastic
draw of random values are likely similar, we grouped these stocks (10 per
factorial cell) in the cross-validation process into either the training or
testing split. Since mPRM is built on the RAM Legacy Stock Assessment database,
when testing model performance on the stock assessment database, we refit mPRM
on each training split.

@@

Ensemble models, and in particular the machine learning ensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning ensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These ensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning ensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting the trends of status (SSCOM; Fig.
\ref{performance-sim-slope}).

<!--TODO: check labels on Figure S4 – repeat of (d) and missing (f)-->
The ensemble models were able to improve the predictions of status by
exploiting the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high prediction
clusters (Fig. \ref{partial-sim}). Ensembles also exploited the covariance
between individual model predictions. For instance, both the linear model and
GBM ensemble suggest that if mPRM and SSCOM predict high status, the true
status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The
addition of spectral density covariates helped the ensemble models correctly
predict higher status values (Fig. \ref{hexagon}g, h) by exploiting
interactions between the spectral density predictors and the individual model
predictions (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally
degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

When applied to the stock assessment database, the ensemble models---trained
exclusively on the simulated dataset---generally performed as well or better
than the best individual models. The mean, random forest, and GBM ensembles
even outperformed the mPRM method which is trained directly on the RAM Legacy Stock
Assessment database itself (Fig. \ref{performance}b, Fig. \ref{hexagon-ram}).
Compared to the individual models, the machine learning ensembles increased
accuracy by `r mean_ram$mach_vs_ind_mare_fold`%, 
improved correlation from `r mean_ram$ind_corr_range` to 
`r mean_ram$mach_corr_range`, and reduced bias from
`r mean_ram$ind_mre_range` to `r mean_ram$mach_mre_range`.

@@

Ensemble methods provide a useful approach to situations where conservation and
ecological resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status---a situation common to many
ecological settings beyond fisheries. Compared to individual models of fish
population status, ensemble methods were consistently the best or among the best
across three performance dimensions (accuracy, bias, and rank-order
performance), two response variables (status and trajectory), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a
simple average to machine learning models). Our results suggest choosing an
superensemble model that allows for non-parametric relationships, such as machine
learning methods. These methods provide added insight into individual model
behaviour and generally performed the best, however even a simple average of
predictions across multiple models may be useful.

@@

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble models
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. By focussing on
predictions, ensembles do not suffer from the muddled inference of coefficient
averaging when coefficients covary [@cade2015] and are a more general purpose
tool: they do not require information theoretics, they can combine different
types of models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of superensembles is that they can be tailored to specific response
variables. For example, we built separate ensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For example, SSCOM contributed little to the GBM ensemble estimate
of status at higher levels of predicted $B/B_\mathrm{MSY}$, but contributed
strongly to estimates of slope (TODO FIG). Formally, fitting ensemble models to
specific quantities of interest provides an additional calibration step
[@rykiel1996]. Individual models are typically calibrated (i.e. parameters are
estimated) based on a single response variable; however, this model might then
provide a biased or inaccurate estimate of other quantities of interest. For
example, a data-limited fisheries model might calibrate parameters by
maximizing likelihood with respect to observed and predicted catches but those
parameters may then provide a biased or inaccurate estimate of the mean and
slope of $B/B_\mathrm{MSY}$. Ensemble methods provide a final calibration step
to a quantity of interest. This ensemble calibration could further include a
loss function tailored to the goals of the model, say placing greater weight on
accuracy at low status levels than higher values.

* Coilin: How ensembles can help understand mechanistic underpinnings of individual 
  models
    * discover surprises: counterintuitive relationships and interactions
    * can dig into surprising conditions and learn about why certain models fail; 
      potentially learn how to improve models
    * can learn under what conditions certain models perform well
    * pick out an example

Combining predictions from multiple models via superensemble methods is also
broadly useful in other subfields of ecology and fisheries science. Predictions
about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international (e.g. the
IUCN Red List, [@iucn2015]) levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of species risk [e.g. @anderson2011a; @pinsky2011] (*TODO instead
get references from official national/international risk assessments?*), or
population dynamics models to data for individual species [e.g. @dfo2010].
Both types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk (e.g., coefficient
averaging, [@burnham2002], generalized modeling [@yeakel2011], or
semi-parametric methods, [@thorson2014]), ensemble methods are a relatively
simple way to combine predictions in a transparent manner. Beyond estimates of
status and trajectory, ensemble methods could be used to increase the robustness
of spatial predictions when designing networks of protected areas
[@rassweiler2014], or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].

@@

-->

@@

TODO *Example: AB carried out the molecular lab work, participated in data
analysis, carried out sequence alignments, participated in the design of the
study and drafted the manuscript; CD carried out the statistical analyses; EF
collected field data; GH conceived of the study, designed the study,
coordinated the study and helped draft the manuscript. All authors gave final
approval for publication.*

>>>>

\noindent
^5^NOAA/Northeast Fisheries Science Center, Ecosystem Assessment Program, 166 Water St., 
Woods Hole, MA, 02543, USA

@@

Ecological resource managers are often faced with reconciling multiple potentially
conflicting estimates of population status and trajectory.  One solution is to
average these predictions in an ensemble, but this approach ignores covariance
between models and may not optimally reduce bias and improve accuracy.
Superensemble models, commonly used in the fields of climate and weather
science, may provide a superior solution. Superensembles use the predictions
from multiple models as covariates in a new statistical model. Here we evaluate
the potential for ensemble and superensemble models ('ensemble methods') to improve estimates of fish population
status and trajectory. We fit four data-limited models of population and exploitation
dynamics to marine fish stocks and combine their estimates of the mean and
slope of biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with an
ensemble average and three superensembles: a linear model, a random forest, and
a boosted regression tree. 
We selected data-limited models for their applicability across the majority of stocks world wide.
We build our models on a simulated dataset of 5760
fish stocks and tested them with cross-validation and a global database of 
`r ram_stocks_n` stock assessments that have also been assessed with more data-intensive stock assessment models.
We find that ensemble methods substantially improve estimates of population status and trajectory.
Machine-learning superensembles performed the best for population status: accuracy improved
`r mean_sim$mach_vs_ind_mare_fold`%, correlation between predicted and true
status improved from 
`r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median
proportional error) declined from 
`r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. 
We found similar improvements when predicting the trajectory of status. When the
simulation-trained superensembles were applied to catch data for global fish stocks, the best
superensembles improved all dimensions of performance over the next-best
individual model. Ensemble methods have the potential to
improve estimates of population status and trajectory across many taxa beyond
fish. However, they must be carefully tested, formed from a diverse set of
accurate models, and built on a dataset sufficiently representative of the
populations to which they are applied.

@@

Population status and trajectory are two of the most fundamental values to quantify in ecological resource management [e.g. @mace2008; @iucn2015]. These properties are key to everything from global assessments of extinction risk [e.g. @stuart2004; @schipper2008; @juan-jorda2011] to setting hunting (REF) and fishing limits [e.g. @worm2009] (REFs). However, ecological resource managers are often faced with reconciling multiple uncertain and potentially conflicting estimates of status and trajectory [e.g. @branch2011] (REFs). Some models may suggest a population is at risk and declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of an ensemble of model predictions. Such ensembles are typically more accurate and less biased than individual model estimates and can integrate uncertainty in model structure, initial conditions, and parameter estimation [@dietterich2000; @araujo2007]. This approach forms the basis of many machine learning methods [e.g. @dietterich2000], has helped reconcile climate forecasts from dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are frequently used to improve species distribution modelling [e.g. @araujo2007; @breiner2015] and indeed have been used to combine estimates of population status and trajectory [e.g. @brodziak2010] COSEWIC-IUCN REFS.

<!--
Biological ensemble modeling to evaluate potential futures of living marine resources
Anna Gårdmark1,8, Martin Lindegren2, Stefan Neuenfeldt2, Thorsten Blenckner3, Outi Heikinheimo4, Bärbel Müller-Karulis3,5, Susa Niiranen3, Maciej T. Tomczak3, Eero Aro4, Anders Wikström6, and Christian Möllmann7
Read More: http://www.esajournals.org/doi/abs/10.1890/12-0267.1
-->

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The truth does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called 'superensemble' modelling, is common in climate and weather forecasting [e.g. @krishnamurti1999; @yun2005; @mote2015]. The superensemble is fit to some training dataset where outcomes are well known and used to predict on a dataset of interest. For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

@@

In fisheries science, the gold standard for determining status and trajectory
of exploited fish populations are stock assessments that
incorporate all available data (e.g., catches, size and age distributions,
surveys, and tagging information) to quantify values such as 
the biomass that can produce maximum sustainable yield ($B/B_\mathrm{MSY}$).
However, these kinds of data are not available for the majority of stocks
[@fao2014]. Therefore, a number of models have been proposed to assess
$B/B_\mathrm{MSY}$ based on the limited data available for the majority of
stocks: catches and a basic understanding of population productivity [e.g.
@vasconcellos2005; @martell2013]. Recently, @rosenberg2014 investigated the
performance of four data-limited models through a large-scale simulation
experiment. The four models frequently disagreed about population status and
any one model had relatively poor predictive ability on average (e.g. Fig.
\ref{motivate}).

Here, we estimate population status and trajectory of exploited fish
populations using ensembles and superensembles (collectively 'ensemble
methods') of these four data-limited models. We explore a variety of approaches
applied to both simulated and real-world fish stocks and compare predictive
performance. We find that ensembles, and in particular superensembles,
generally improved predictive performance of status and trajectory of fish
populations over any single model---especially when considered across multiple
dimensions of predictive ability. Furthermore, the output from superensembles
can aid mechanistic understanding of how individual models of status and
trajectory perform.

@@

We first developed and tested ensemble methods with a fully factorial simulated
dataset [@rosenberg2014] with precisely known status. These published simulations included three life
histories: small pelagic, demersal, and large pelagic; three levels of how
depleted biomass was at the start of the dataset compared to carrying capacity:
100%, 70%, and 40% of carrying capacity; and four exploitation dynamics: a
constant exploitation rate, an exploitation rate coupled with biomass to mimic
an open-access single-species fishery, a scenario where exploitation rate
increases to a fixed level, and a 'roller-coaster' scenario where the
exploitation rate increases and then decreases cyclically. Process noise was
introduced to the models through two levels of multiplicative recruitment
variability: $N(0, 0.2)$ and $N(0, 0.6)$, and was either
uncorrelated or had a first-order autoregressive correlation of $0.6$. The
simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year,
$B_t$ represents biomass at time $t$, $r$ represents the intrinsic population
growth rate, $B_0$ represents unfished biomass or carrying capacity $K$, and $C$
represents catch. @rosenberg2014 provide a full summary of
these four methods and code to fit all the models is available in an
accompanying package `datalimited` for the statistical software \textsf{R}. In
summary:

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer biomass
  dynamics [@martell2013]. It requires a prior distribution for $r$ and assigns
  a prior to the relative proportion of biomass at the end compared to unfished
  biomass (depletion) based on the percentage of maximum catch at the end of the
  time series. Our version of the model was modified from @martell2013 to
  generate biomass trends from all viable $r$-$K$ pairs and produced an estimate of
  $B/B_\mathrm{MSY}$ from the geometric mean trend.

@@

$$
\hat{\theta} = 
\argmin_\theta \left( L(b \, | \, \hat{b}_{\mathrm{ensemble}}) \right)
$$
$$
\hat{b}_\mathrm{ensemble} = 
f \left( \hat{b}_\mathrm{CMSY}, \, \hat{b}_\mathrm{COM-SIR}, \,
\hat{b}_\mathrm{SSCOM}, \, \hat{b}_\mathrm{mPRM}, \,
S(0.2), \, S(0.5) \, | \, \theta \right)
$$

@@

We fit the linear model superensemble with second-order interactions. We fit two
machine learning superensemble models based on regression trees. Regression trees
sequentially determine what value of a predictor best splits the response data
into two 'branches' based on a specified loss function [@breiman1984]. In random
forests, a series of regression trees are built on a random subset of the data
and random subset of the covariates of the model [@breiman2001]. In generalized
boosted models (GBMs), each subsequent model is fit to the residuals from the
previous model; data points that are fit poorly in a given model are given more
weight in the next model [@elith2008]. Random forests and GBMs can provide
strong predictive performance and fit highly non-linear relationships
[@elith2008; @hastie2009]. We fit random forest models with the `randomForest`
package [@liaw2002] for \textsf{R} with the default argument values. We fit
boosted regression tree models with the `gbm` package [@ridgeway2015] for
\textsf{R}. Based on cross-validation with the **caret** \textsf{R} package, we
fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate
(shrinkage parameter) of $0.01$, and all other arguments at their default
values.

@@

A critical component to any predictive modelling exercise is to evaluate the
performance of a model on new data [@hastie2009]. We used repeated three-fold
cross validation to test predictive performance: we randomly divided the
dataset into three sets, built superensemble models on two-thirds of the data, and
evaluated predictive performance on the remaining third. We repeated this
across each of the three splits and then repeated the whole procedure 50 times
to account for bias that may result from any one set of validation splits.
Since the dynamics of simulated populations differing only in the stochastic
draw of random values are likely similar, we grouped these stocks (10 per
factorial cell) in the cross-validation process into either the training or
testing split. Since mPRM is built on the RAM Legacy Stock Assessment database,
when testing model performance on the stock assessment database, we refit mPRM
on each training split.

@@

Ensemble methods, and in particular the machine learning superensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning superensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These superensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning superensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting the trends of status (SSCOM; Fig.
\ref{performance-sim-slope}).

<!--TODO: check labels on Figure S4 – repeat of (d) and missing (f)-->
The superensemble models were able to improve the predictions of status by
exploiting the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high prediction
clusters (Fig. \ref{partial-sim}). Superensembles also exploited the covariance
between individual model predictions. For instance, both the linear model and
GBM ensemble suggest that if mPRM and SSCOM predict high status, the true
status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The
addition of spectral density covariates helped the superensemble models correctly
predict higher status values (Fig. \ref{hexagon}g, h) by exploiting
interactions between the spectral density predictors and the individual model
predictions (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally
degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

When applied to the stock assessment database, the superensemble models---trained
exclusively on the simulated dataset---generally performed as well or better
than the best individual models. The mean, random forest, and GBM ensembles
outperformed the mPRM method which is trained directly on the RAM Legacy Stock
Assessment database itself (Fig. \ref{performance}b, Fig. \ref{hexagon-ram}).
Compared to the individual models, the machine learning superensembles increased
accuracy by `r mean_ram$mach_vs_ind_mare_fold`%, 
improved correlation from `r mean_ram$ind_corr_range` to 
`r mean_ram$mach_corr_range`, and reduced bias from
`r mean_ram$ind_mre_range` to `r mean_ram$mach_mre_range`.

@@

Ensemble methods provide a useful approach to situations where conservation and
ecological resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status---a situation common to many
ecological settings beyond fisheries. Compared to individual models of fish
population status, ensemble methods were consistently the best or among the best
across three performance dimensions (accuracy, bias, and rank-order
performance), two response variables (status and trajectory), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a
simple average to machine learning superensembles). Our results suggest choosing an
superensemble model that allows for non-parametric relationships, such as machine
learning methods. These methods provide added insight into individual model
behaviour and generally performed the best, however even a simple average of
predictions across multiple models may be a robust solution compared to picking
any one model.

@@

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. By focussing on
predictions, ensembles do not suffer from the muddled inference of coefficient
averaging when coefficients covary [@cade2015] and are a more general purpose
tool: they do not require information theoretics, they can combine different
types of models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of superensembles is that they can be tailored to predict specific response
variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For example, SSCOM contributed little to the GBM superensemble estimate
of status at higher levels of predicted $B/B_\mathrm{MSY}$, but contributed
strongly to estimates of slope (TODO FIG). Formally, fitting superensemble models to
specific quantities of interest provides an additional calibration step
[@rykiel1996]. Individual models are typically calibrated (i.e. parameters are
estimated) based on a single response variable; however, this model might then
provide a biased or inaccurate estimate of other quantities of interest. For
example, a data-limited fisheries model might calibrate parameters by
maximizing likelihood with respect to observed and predicted catches but those
parameters may then provide a biased or inaccurate estimate of the mean and
slope of $B/B_\mathrm{MSY}$. Ensemble methods provide a final calibration step
to a quantity of interest. This ensemble calibration could further include a
loss function tailored to the goals of the model, say placing greater weight on
accuracy at low status levels than higher values.

*TODO: Coilin: How ensembles can help understand mechanistic underpinnings of individual models*
Beyond predictive performance, superensembles can help understand mechanistic
underpinnings of individual models. 
First, at a most basic level, superensembles that allow for nonlinear
relationships can describe at what ranges of a prediction a certain model is
most informative. For example, we can see that SSCOM is most effective at
distinguishing low values of $B/B_\mathrm{MSY}$ (Fig. S4).
Second, the interaction between superensemble predictors can highlight
under what conditions certain models perform best. 
For instance, SAY SOMETHING ABOUT FIG S5 or FIG S6.
*discover surprises: counterintuitive relationships and interactions*
*can dig into surprising conditions and learn about why certain models fail; potentially learn how to improve models*
*can learn under what conditions certain models perform well*

Combining predictions from multiple models via superensemble methods is also
broadly useful in other subfields of ecology and fisheries science. Predictions
about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g. the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of species risk [e.g. @anderson2011a; @pinsky2011], or
population dynamics models to data for individual species [e.g. @dfo2010].
Both types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk (e.g., coefficient
averaging, [@burnham2002], generalized modeling [@yeakel2011], or
semi-parametric methods, [@thorson2014]), ensemble methods are a relatively
simple way to combine predictions in a transparent manner. Beyond estimates of
status and trajectory, ensemble methods could be used to increase the robustness
of spatial predictions when designing networks of protected areas
[@rassweiler2014], or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].

@@

@@

TODO *Example: AB carried out the molecular lab work, participated in data
analysis, carried out sequence alignments, participated in the design of the
study and drafted the manuscript; CD carried out the statistical analyses; EF
collected field data; GH conceived of the study, designed the study,
coordinated the study and helped draft the manuscript. All authors gave final
approval for publication.*
-->
